### 2024-08-04 conteudo/preliminar/results.tex
add table
add base cro because of error

Related to our RQ1
(\textit{How effective is our approach in mitigating duplicate code in the Linux kernel?}),
we intend to approach our ethnographic study presented in \ref{sec:meteth} as the next steps 
in our work. As an early validation to see the potential of this research, we conducted the 
proposed systematic approach to mitigate code duplication on two function pairs. Table
(CREATE TABLE AND ADD HERE) shows the early results found.

CREATE TABLE AND ADD HERE

@@

As shown in our proposed schedule (Figure CREATE FIGURE AND ADD HERE), as we advance, 
we intend to do the proper ethnographic study, starting by completing our systematic 
approach to mitigate code duplications, and with this mitigation on hands we intend 
to process to send them to the AMD Display driver mailing list to understand the 
AMD Display driver maintainers about the mitigations made by us.

>>>>

Related to our RQ1
(\textit{How effective is our approach in mitigating duplicate code in the Linux kernel?}),
we intend to approach our ethnographic study presented in \ref{sec:meteth} as the next steps 
in our work. As an early validation to see the potential of this research, we conducted the 
proposed systematic approach to mitigate code duplication on two function pairs. Table
\ref{tab:patch} shows the early results found.

\input{conteudo/preliminar/table_patch}

@@

As shown in our proposed schedule \ref{fig:cronograma}, as we advance, 
we intend to do the proper ethnographic study, starting by completing our systematic 
approach to mitigate code duplications, and with this mitigation on hands we intend 
to process to send them to the AMD Display driver mailing list to understand the 
AMD Display driver maintainers about the mitigations made by us.

\input{conteudo/preliminar/cronograma}
